Interfering with Noninterference \iftext\thanks{\bcp{Identify applicable funding agencies here (DARPA and NSF and...?)}}\fi

### 2020-05-24 props.tex
props.tex contains a slightly more honest treatment of calls and returns, and I think it works properly now.

    Values are words:
    \[w \in \mathcal{W}\]

@@

    Execution is by a step function \(\cdot \xrightarrow{\cdot} \cdot : \mathcal{M} \rightarrow
    \mathit{Obs} \times \mathcal{M}\). For every machine state \(m\) there is exactly one \(o\) and \(m'\)
    such that \(m \xrightarrow{o} m'\).

    Meanwhile a policy tracks a mix of static and dynamic enforcement. A policy consists of
    a set of policy states, \(p \in \mathcal{P}\), a policy initializer
    \(pinit : \mathcal{M} \rightharpoonup \mathcal{P}\), and a policy-parameterized step relation
    \(\cdot, \cdot \xrightarrow{\cdot}_P \cdot, \cdot : \mathcal{M} \times \mathcal{P} \rightharpoonup
    \mathit{Obs} \times \mathcal{M} \times \mathcal{P}\) such that if \(m,p \xrightarrow{o}_P m',p'\),
    then \(m \xrightarrow{o} m'\). The initializer is a partial function from machine states to policy
    states, reflecting that a policy may apply static constraints on the initial state. The parameterized
    step relation is likewise partial to allow for fail-stop behavior.

@@

@@

      [TODO: be more explicit about what the call map does]
      A state \(m_c\) is a {\it call state} if [call map says it is], and a state \(m_p\) is
      considered to have returned to \(m_c\) if [etc.] From a call state with \(n\) arguments to
      its call, we can construct a contour that should apply inside the call:
      \[Cof(m)(k) =
      \begin{cases}
        (\mathtt{HC},\mathtt{HI}) & \text{if } k \in \mathcal{W}
                                    \text{ and } k \leq m(\mathtt{SP}) - n \\
        (\mathtt{HC},\mathtt{LI}) & \text{if } k \in \mathcal{W}
                                    \text{ and } k \leq m(\mathtt{SP}) \\
        (\mathtt{LC},\mathtt{LI}) & \text{else} \\
      \end{cases}\]

      Above the stack pointer, memory is high integrity in an extension of safe initialization;
      from the perspective of the callee, that memory is not initialized. Below the old stack
      pointer, memory is high integrity and high confidentiality. Registers and the callee's
      frame are low integrity and low confidentiality. These categories inform our integrity
      and confidentiality properties.

@@

      A system enjoys observable integrity if for any initial state \(m_0\), call state \(m_c\),
      policy state \(p_c\), and contour \(C = Cof(m_c)\) such that \(m_0,\mathit{pinit}(m_0)
      \hookrightarrow \dots (m_c,p_c) \dots\):

      \begin{itemize}
        \item If \((m_c,p_c) \hookrightarrow \dots (m_r,p_r) | \mathit{returned}\ m_c\ m_r\):
          \begin{itemize}
            \item Let \(m_r' = \mathit{roll}_I(C,m_c,m_r)\), \((m_r,p_r) \rightsquigarrow O\), and
              \(m_r' \rightsquigarrow O'\)
            \item If \(m_r,p_r \hookrightarrow MP \in \top\) then \(O \simeq O'\)
            \item Otherwise \(O \lesssim O'\)
          \end{itemize}
      \end{itemize}

@@

      An eager enforcement mechanism implements a stronger property, which we term {\it eager integrity}.
      Eager integrity simplifies observable integrity by requiring that high integrity data of \(m_r\) be
      identical to that of \(m_c\). Formally, a systemctl enjoys eager integrity if for any initial state
      \(m_0\), call state \(m_c\), policy state \(p_c\), and contour \(C = Cof(m_c)\) such that
      \(m_0,\mathit{pinit}(m_0) \hookrightarrow \dots (m_c,p_c) \dots (m_r,p_r) \dots\), where \(\mathit{returned}\ m_c\ m_r\):

@@

      A system enjoys observable confidentiality if for any initial state \(m_0\), call states \(m_c\)
      and \(m_c'\), policy state \(p_c\), and contour \(C = Cof(m_c)\) such that \(m_0,\mathit{pinit}(m_0)
      \hookrightarrow \dots (m_c,p_c) \dots\) and \(m_c \approx_C m_c'\):

      \begin{itemize}
        \item If \((m_c,p_c) \hookrightarrow MP (m_r,p_r) | \mathit{returned}\ m_c\ m_r\)
          \begin{itemize}
            \item Then there is some \(m_r'\) where
              \(m_c' \hookrightarrow M m_r' | \mathit{returned}\ m_c'\ m_r'\)
            \item Let \(m_r'' = \mathit{roll}_C(C,m_c,m_r,m_c',m_r')\),
              \((m_r,p_r) \rightsquigarrow O\), and \(m_r'' \rightsquigarrow O'\)
            \item If \(m_r,p_r \hookrightarrow_P MP \in \top\) then \(O \simeq \mathit{ObsOf}(M) +\!\!\!+ O'\)
            \item Otherwise \(O \lesssim \mathit{ObsOf}(M) +\!\!\!+ O'\)
          \end{itemize}
        \item Else, let \(m_c,p_c \rightsquigarrow O\) and \(m_c' \rightsquigarrow O'\)
          \begin{itemize}
            \item If \(m_c,p_c \hookrightarrow_P MP \in \top\) then \(O \simeq O'\)
            \item Otherwise \(O \lesssim O'\)
          \end{itemize}
      \end{itemize}

@@

      Once again an eager policy enforces a stronger property that only concerns the behavior of
      the original trace and its variant within each call. A system enjoys {\it eager stack
      confidentiality} if, for any initial state \(m_0\), call states \(m_c\) and \(m_c'\),
      policy state \(p_c\), and contour \(C = Cof(m_c)\) such that \(m_0,\mathit{pinit}(m_0) \hookrightarrow
      \dots (m_c,p_c) \dots\) and \(m_c \approx_C m_c'\):

      \begin{itemize}
        \item If \((m_c,p_c) \hookrightarrow_P MP (m_r,p_r) | \mathit{returned}\ m_c\ m_r\)
          \begin{itemize}
            \item Then there is some \(m_r'\) where
              \(m_c' \hookrightarrow M m_r' | \mathit{returned}\ m_c'\ m_r'\)
            \item \(\mathit{ObsOf}(MP) \simeq \mathit{ObsOf}(M)\)
            \item And for all \(k\), if \(m_c(k) \not = m_r(k)\) or \(m_c'(k) \not = m_r'(k)\),
              \(m_r(k) = m_r'(k)\)
          \end{itemize}
        \item Else, let \(m_c,p_c \rightsquigarrow O\) and \(m_c' \rightsquigarrow O'\)
          \begin{itemize}
            \item If \(m_c,p_c \hookrightarrow_P MP \in \top\) then \(O \simeq O'\)
            \item Otherwise \(O \lesssim O'\)
          \end{itemize}
      \end{itemize}

>>>>

    Values and addresses are words:
    \[a,w \in \mathcal{W}\]

@@

    Execution is by a step function \(m \xrightarrow{o} m' : m \in \mathcal{M} \rightarrow
    o \in \mathit{Obs} \times m' \in \mathcal{M}\).

    A policy tracks a mix of static and dynamic enforcement. A policy consists of
    a set of policy states, \(p \in \mathcal{P}\), a policy initializer
    \(pinit : \mathcal{M} \rightharpoonup \mathcal{P}\), and a policy-parameterized step function:
    \[m, p \xrightarrow{o}_P m', p' : m \in \mathcal{M} \times p \in \mathcal{P} \rightharpoonup
    o \in \mathit{Obs} \times m' \in \mathcal{M} \times p' \in \mathcal{P}\]

    Axiomatically, if \(m,p \xrightarrow{o}_P m',p'\), then \(m \xrightarrow{o} m'\).
    The initializer is a partial function from machine states to policy
    states, reflecting that a policy may apply static constraints on the initial state. The parameterized
    step relation is likewise partial to allow for fail-stop behavior.

@@

  \paragraph{Calling Conventions and Contours}

      A subroutine call with \(n\) arguments follows the following convention:

      \begin{itemize}
        \item The stack pointer is increased by \(n+1\)
        \item A {\tt Jal} occurs
        \item The return address is stored at \(\mathtt{SP} - 1\)
      \end{itemize}

      The final state of a call sequence is a {\it call state}. If \(M\) is a call sequence with
      we map it to its call state, number of arguments, and the PC and SP values of its eventual
      return by the function \(\mathit{call} : \mathit{trace}\ \mathcal{M} \rightharpoonup \mathcal{M}
      \times \mathbb{N} \times \mathcal{W} \times \mathcal{W}\). We can also track a call sequence in the
      policy state, defining \(\mathit{call}_P : \mathcal{M} \times \mathcal{P} \rightharpoonup \mathbb{N}
      \times \mathcal{W} \times \mathcal{W}\) such that:

      \[\frac{m_0,\mathit{pinit}(m_0) \hookrightarrow_P \dots m,p \dots \hspace{.5cm}
              m_0 \hookrightarrow \dots M \dots \hspace{.5cm} \mathit{call}(M) = m, n, a_{pc}, a_{sp}}
             {\mathit{call}_P(m,p) = n, a_{pc}, a_{sp}}\]

      A state is considered to have returned after a call if the stack pointer is the same as before the call
      (\(a_{sp}\)) and the program counter is the next address after (\(a_{pc}\)):
      \[\mathit{returned}\ m\ a_{pc}\ a_{sp} \triangleq m'(\mathtt{SP}) = a_{sp} \land m(\mathtt{PC}) = a_{pc}\]

@@

      When \(m,p\) is a call state \(\mathit{call}_P(m,p) = n,\_,\_\) for some \(n\),
      we can construct a contour based on the size of \(m\)'s stack frame, as follows:
      \[Cof(m,n)(k) =
      \begin{cases}
        (\mathtt{HC},\mathtt{HI}) & \text{if } k \in \mathcal{W}
                                    \text{ and } k \leq m(\mathtt{SP}) - n \\
        (\mathtt{HC},\mathtt{LI}) & \text{if } k \in \mathcal{W}
                                    \text{ and } k \geq m(\mathtt{SP}) \\
        (\mathtt{LC},\mathtt{HI}) & \text{if } k \in \mathcal{W}
                                    \text{ and } k = m(\mathtt{SP}) - 1 \\
        (\mathtt{LC},\mathtt{LI}) & \text{else} \\
      \end{cases}\]

      Above the stack pointer, memory is high integrity in an extension of safe initialization;
      from the perspective of the callee, that memory is not initialized. Below the old stack
      pointer, memory is high integrity and high confidentiality. The top of the callee's frame
      is its return address, which it must be able to read in order to return but which is
      high integrity [does this make sense?] Registers and the callee's frame are low integrity
      and low confidentiality. These categories inform our integrity and confidentiality properties.

@@

      A system enjoys observable integrity if for any initial state \(m_0\), call state \(m_c\),
      and policy state \(p_c\) such that \(m_0,\mathit{pinit}(m_0) \hookrightarrow \dots (m_c,p_c) \dots\)
      and \(\mathit{call}_P(m_c,p_c) = n,a_{pc},a_{sp}\):

      \begin{itemize}
        \item If \((m_c,p_c) \hookrightarrow \dots (m_r,p_r) | \mathit{returned}\ m_r\ a_{pc}\ a_{sp}\):
          \begin{itemize}
            \item Let \(C = \mathit{Cof}(m_c,n)\)
            \item Let \(m_r' = \mathit{roll}_I(C,m_c,m_r)\), \((m_r,p_r) \rightsquigarrow O\), and
              \(m_r' \rightsquigarrow O'\)
            \item If \(m_r,p_r \hookrightarrow MP \in \top\) then \(O \simeq O'\)
            \item Otherwise \(O \lesssim O'\)
          \end{itemize}
      \end{itemize}

@@

      An eager enforcement mechanism implements a stronger property, which we term {\it eager integrity}.
      Eager integrity simplifies observable integrity by requiring that high integrity data of \(m_r\) be
      identical to that of \(m_c\). Formally, a system enjoys eager integrity if for any initial state
      \(m_0\), call state \(m_c\), and policy state \(p_c\) such that \(\mathit{call}(m_c,p_c) =
      n, a_{pc}, a_{sp}\), and some \(m_r\) and \(p_r\) such that
      \(m_0,\mathit{pinit}(m_0) \hookrightarrow \dots (m_c,p_c) \dots (m_r,p_r) | \mathit{returned}\ m_r\ a_{pc}\ a_{sp}\):

@@

      A system enjoys observable confidentiality if for any initial state \(m_0\), call state \(m_c\),
      and policy state \(p_c\) such that \(m_0,\mathit{pinit}(m_0) \hookrightarrow \dots (m_c,p_c) \dots\) and
      \(\mathit{call}(m_c,p_c) = n, a_{pc}, a_{sp}\):

      \begin{itemize}
        \item Let \(C = \mathit{Cof}(m_c,n)\)
        \item For all \(m_c'\) such that \(m_c \approx_C m_c'\):
        \item If \((m_c,p_c) \hookrightarrow MP (m_r,p_r) | \mathit{returned}\ m_r\ a_{pc}\ a_{sp}\)
          \begin{itemize}
            \item Then there is some \(m_r'\) where
              \(m_c' \hookrightarrow M m_r' | \mathit{returned}\ m_r'\ a_{pc}\ a_{sp}\)
            \item Let \(m_r'' = \mathit{roll}_C(C,m_c,m_r,m_c',m_r')\),
              \((m_r,p_r) \rightsquigarrow O\), and \(m_r'' \rightsquigarrow O'\)
            \item If \(m_r,p_r \hookrightarrow_P MP \in \top\) then \(O \simeq \mathit{ObsOf}(M) +\!\!\!+ O'\)
            \item Otherwise \(O \lesssim \mathit{ObsOf}(M) +\!\!\!+ O'\)
          \end{itemize}
        \item Else, let \(m_c,p_c \rightsquigarrow O\) and \(m_c' \rightsquigarrow O'\)
          \begin{itemize}
            \item If \(m_c,p_c \hookrightarrow_P MP \in \top\) then \(O \simeq O'\)
            \item Otherwise \(O \lesssim O'\)
          \end{itemize}
      \end{itemize}

@@

      Once again an eager policy enforces a stronger property that only concerns the behavior of
      the original trace and its variant within each call. A system enjoys {\it eager stack
      confidentiality} if, for any initial state \(m_0\) and call state \(m_c\) such that
      \(m_0,\mathit{pinit}(m_0) \hookrightarrow \dots (m_c,p_c) \dots\) and
      \(\mathit{call}(m_c,p_c) = n, a_{pc}, a_{sp}\):

      \begin{itemize}
        \item Let \(C = \mathit{Cof}(m_c,n)\)
        \item For all \(m_c'\) such that \(m_c \approx_C m_c'\):
        \item If \((m_c,p_c) \hookrightarrow_P MP (m_r,p_r) | \mathit{returned}\ m_r\ a_{pc}\ a_{sp}\)
          \begin{itemize}
            \item Then there is some \(m_r'\) where
              \(m_c' \hookrightarrow M m_r' | \mathit{returned}\ m_c'\ m_r'\)
            \item \(\mathit{ObsOf}(MP) \simeq \mathit{ObsOf}(M)\)
            \item And for all \(k\), if \(m_c(k) \not = m_r(k)\) or \(m_c'(k) \not = m_r'(k)\),
              \(m_r(k) = m_r'(k)\)
          \end{itemize}
        \item Else, let \(m_c,p_c \rightsquigarrow O\) and \(m_c' \rightsquigarrow O'\)
          \begin{itemize}
            \item If \(m_c,p_c \hookrightarrow_P MP \in \top\) then \(O \simeq O'\)
            \item Otherwise \(O \lesssim O'\)
          \end{itemize}
      \end{itemize}
